### 2016-10-19 Manuscript/SW_early_life_telomeres.Rmd
Home edits

temp <- subset(dd,Ageclass !='CH')

ggplot(temp,aes(x = Insect,y = RTL))+
geom_boxplot(aes(group = Insect))+
geom_smooth()+
theme_bw()

dd$LogAge <- log(dd$Agemonths)
m1 <- lmer(RTL~LogAge+(1|BirdID),data=dd)
m2 <- lmer(RTL~LogAge+(1|BirdID)+(1|TerritoryID),data=dd)
m3 <- lmer(RTL~LogAge+(1|BirdID)+(1|LayYear),data=dd)
m4 <- lmer(RTL~LogAge+(1|BirdID)+(1|CatchYear)+(1|LayYear),data=dd)

anova(m1,m2,m3,m4)

head(dd3)
fit <- coxph(Surv(RemainingLife, RemainingLife1, Died1) ~ Agemonths1 + RTL1,
              data=dd3)

 dd3 <- subset(dd3,RemainingLife-RemainingLife1 >0)

which(is.na(dd3$RemainingLife1))
which(is.na(dd3$RTL1))

plot(DeltaRTL~DeltaAge,data=dd3)

summary(lm(DeltaRTL~DeltaInsect,data=subset(dd3,Ageclass !='A'),na.action=na.exclude))
summary(lm(RTL~Insect,data=juv,na.action=na.exclude))

ggplot(dd3,aes(x = DeltaInsect,y = DeltaRTL,col = Ageclass))+
geom_point()+
stat_smooth(method = 'lm')

>>>>

temp <- subset(dd3,BirdID %in% juv$BirdID)
nrow(temp)

### 2016-10-19 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd
Home edits

temp <- subset(juv_r,Season == 'Major')
Fig3C <- ggplot(temp,
       aes(
           y = RTL,
           x=yday,
       col = (Ageclass))) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'top') +
  geom_point()+
   stat_smooth(method = 'lm',formula = y~poly(x,2))+
  # scale_colour_manual(values = c('grey','darkorange','darkgreen'))+
  # scale_fill_manual(values = c('grey','darkorange','darkgreen'))+
  annotate('text',x = 3,y = 2.1,label = 'C')

>>>>

temp <- dd
Fig3C <- ggplot(temp,
       aes(
           y = RTL,
           x=Insect)) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'top') +
  geom_point()+
   stat_smooth(method = 'lm')+
  # scale_colour_manual(values = c('grey','darkorange','darkgreen'))+
  # scale_fill_manual(values = c('grey','darkorange','darkgreen'))+
  annotate('text',x = 3,y = 2.1,label = 'C')
